Word2vec learns effective distance of scientific co-affiliation

### 2020-01-27 paper/current/main.tex
updated figure text, added supporting figure for gravity correlation

%
% Figure - Gravity law performance
%
\begin{figure}[h!]
	\centering
	\label{fig:gravity_performance}
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance.pdf}
	\caption{
		\textbf{Embedding proximity outperform and are more robust than geographic distance.}
		Embedding proximity (\textbf{a}) explains more of the total distance than does geographic distance (\textbf{b}). 
		Red line is line of best fit. 
		Black dots are mean flux across binned proximity meas.
		Predictions  of flux between organization pairs made using embedding proximity (\textbf{c}) out-perform those made using geographic distance (\textbf{d}). 
		Boxplots show distirbution of actual flux for binned values of predicted flux.
		Box color corresponds to the degree to which the distribution overlaps $x = y$.
		Predictions made for only pairs of organizations within the same country using embedding proximity (\textbf{e}) outperform those made for geographic distance (\textbf{f}).
		Embedding proximity (\textbf{g}) also outperforms geographic distance (\textbf{h}) when predicting flux between only pairs of organizations in different countries. 
	}
\end{figure}

@@

\newpage
\printbibliography{}

>>>>

%
% Figure - Gravity law performance
%
\begin{figure}[h!]
	\centering
	\label{fig:gravity_performance}
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance.pdf}
	\caption{
		\textbf{Embedding proximity outperform and are more robust than geographic distance.}
		\textbf{a.} embedding proximity (the cosine similarity between vectors) explains more of the flux between organization pairs than does geographic distance (\textbf{b}). 
		Red line is line of best fit. 
		Black dots are mean flux across binned proximity meas.
		Color indicates frequency of organization pairs within each hex bin.
		\textbf{c-d.} Predictions  of flux between organization pairs made using embedding proximity out-perform those made using geographic distance. 
		Boxplots show distirbution of actual flux for binned values of predicted flux.
		Box color corresponds to the degree to which the distribution overlaps $x = y$.
		\textbf{e-f.} Predictions made for only pairs of organizations within the same country using embedding proximity outperform those made for geographic distance.
		\textbf{g-h.} Embedding proximity also outperforms geographic distance when predicting flux between only pairs of organizations in different countries. 
	}
\end{figure}

@@

\newpage
\section{Supporting Information}

%
% Figure - gravity correlation
%
\begin{figure}[hp!]
	\centering
	\label{fig:projection}
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_correlations.pdf}
	\caption{
		\textbf{Embedding proximity explains more variance for global, within, and between country flux than geographic distance.}
		\textbf{a.}
		Embedding proximity (cosine similarity between vectors) explains more of the total distance than does geographic distance (\textbf{b}). 
		Red line is line of best fit. 
		Black dots are mean flux across binned proximity meas.
		Color indicates frequency of organization pairs within each hex bin.
		Results here are identical to those shown in Fig.~\ref{fig:gravity_performance}a and Fig.~\ref{fig:gravity_performance}.
		\textbf{c-d.}	embedding proximity explains more variance when considering only pairs of organizations within the same country. 
		\textbf{e-f.} embedding proximity more robust than geographic distance for pairs of organizations in different countries. 
	}
\end{figure}

\printbibliography{}
